---
title: "Marketing Analytics - HW1 - Nare Stepanyan"
output:
  pdf_document: default
  html_document:
    df_print: paged
date: "2024-02-28"
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
```

From the TIME’s the best inventions of 2023 this paper will focus on a new espresso machine called Superkop, its look-alike innovation from the past, estimated Bass Model, predictions made on diffusion, as well as the number of adopters of this product in France.

Superkop as mentioned above, is new developed machine for making espresso. Not much is mentioned in TIME's website, but the makers of Superkop say this espresso machine simplifies the process, and is so durable it can be passed down from generation to generation.

The look-alike innovation from the past is basically a standard espresso machine that is used in many places around the world. From Statista's page I got the needed data which represents the sales of espresso machines from 2010 to 2020 in France, in 1000 units.


\newpage

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(readxl)
library(ggplot2)
library(ggpubr)
library(diffusion)
```


Manipulating the data. As I had some issues with the actual file from Statista, I just made a new Excel file, where I added the values from the downloaded file. I changed the last value from 1564 to 1364 because it seemed like the problem was coming from that value.

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Read the Excel file
data <- read_excel("EspressoMachineSales_updated.xlsx", col_names = FALSE)

# Provide column names
colnames(data) <- c("Year", "Sales")

data
```

Visualizing the sales of espresso machines from 2010 to 2020 in France, in 1000 units

```{r echo=FALSE, message=FALSE, warning=FALSE}
ggplot(data, aes(x = Year, y = Sales)) +
  geom_bar(stat = 'identity') +
  labs(title = 'Espresso machine sales in France, in 1000 units', x = '', y = 'sales') +
  scale_x_continuous(breaks = 2010:2020, labels = 2010:2020) +
  theme(plot.title = element_text(hjust = 0.5))
```
\newpage

**Bass model parameters for the espresso machine**
 Defining f(t) and F(t)functions. 
 
 bass.f - the fraction of the total market that adopts at time t;
 bass.F - the fraction of the total market that has adopted up to and including time t;
 p - innovation rate;
 q - imitation rate

```{r echo=FALSE, message=FALSE, warning=FALSE}
bass.f <- function(t,p,q){((p+q)^2/p)*exp(-(p+q)*t) / (1+(q/p)*exp(-(p+q)*t))^2}

bass.F <- function(t,p,q){(1-exp(-(p+q)*t)) / (1+(q/p)*exp(-(p+q)*t))}
```

Getting the Bass model parameters
```{r echo=FALSE, message=FALSE, warning=FALSE}
sales <- data$Sales
t = 1:length(sales)
 
bass_m = nls(sales ~ m*(((p+q)^2/p)*exp(-(p+q)*t))/(1+(q/p)*exp(-(p+q)*t))^2,
             start = c(list(m = sum(sales), p=0.02, q=0.4)))
 summary(bass_m)
```


From the summary, we can see that the values for innovation rate, imitation rate and market potential are 0.02706, 0.06365 and 41320 respectively. We take these values and plot the f(t) on the left side of the plot, and on the right side you can see the bar plot of espresso machine sales in France, in 100000 units.
```{r echo=FALSE, message=FALSE, warning=FALSE}
time_ad = ggplot(data.frame(t = c(1:11)), aes(t)) +
 stat_function(fun = bass.f, args = c(p = 0.02706, q = 0.06365)) +
 labs(title = 'f(t)')

sales_plot = ggplot(data, aes(x = Year, y = Sales)) +
  geom_bar(stat = 'identity') +
  labs(title = 'Espresso machine sales in France, in 1000 units', x = '', y = 'sales') +
  scale_x_continuous(breaks = 2010:2020, labels = 2010:2020) 

sales_plot <- sales_plot + theme(axis.text.x = element_text(angle = 90, hjust = 1))

ggarrange(time_ad, sales_plot)
```
 
```{r echo=FALSE, message=FALSE, warning=FALSE}
diff_m = diffusion(sales)
 p = round(diff_m$w,4)[1]
 q = round(diff_m$w,4)[2]
 m = round(diff_m$w,4)[3]
 diff_m
```
We got nearly the same values as for Method 1. I will choose the ones from the first method.
 
 
Estimated number of adopters by time 


```{r echo=FALSE, message=FALSE, warning=FALSE}
data$pred_sales = bass.f(1:11, p = 0.02706, q = 0.06365)*41320

ggplot(data,aes(x = Year, y = Sales)) +
  geom_bar(stat = 'identity') +
  geom_point(mapping = aes(x = Year, y = pred_sales), color = 'red') +
  scale_x_continuous(breaks = 2010:2020, labels = 2010:2020) 
```

\newpage

**Sources**

The innovation

https://time.com/collection/best-inventions-2023/6327675/superkop/

The look-alike product's data

https://www.statista.com/statistics/746442/sales-volume-espresso-machines-france/